A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain

### 2020-04-20 Environmental-Correlates-of-COVID19-Spain/Environmental-Correlates-of-COVID19-Spain.Rmd
Started working on the results and discussion

---
title: A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Fernando A. Lopez
    email: fernando.lopez@upct.es
    affiliation: Universidad Politecnica de Cartagena
  - name: Tatiane Menezes
    email: tatiane.menezes@ufpe.br
    affiliation: Departamento de Economia
  - name: Renata Cavalcanti
    email: renata.vcsantos@gmail.com
    affiliation: Nucleo de Pesquisa
  - name: Maira Galdino da Rocha Pitta
    email: mgrpitta@ufpe.br
    affiliation: Nucleo de Pesquisa
address:
  - code: McMaster University
    address: School of Geography and Earth Sciences, McMaster University, 1281 Main St W, Hamilton, ON, L8S 4K1, Canada
  - code: Universidad Politecnica de Cartagena
    address: Departamento de Metodos Cuantitativos, Ciencias Juridicas, y Lenguas Modernas, Universidad Politecnica de Cartagena, Calle Real Numero 3, 30201, Cartagena, Murcia, Spain
  - code: Departamento de Economia
    address: Departamento de Economia, Universidade Federal de Pernambuco, Av dos Economistas, s/n - Cidade Universitária, Recife - PE, 50670-901, Brasil  
  - code: Nucleo de Pesquisa
    address: Núcleo de Pesquisa em Inovação Terapêutica NUPIT / UFPE, Av. Prof. Moraes Rego, 1235 - Cidade Universitária, Recife, PE, CEP 50670-901, Brazil  
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature, humidity, and hours of sunshine. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures and higher levels of humidity, although coefficients for this variable are significant only in some equations. Sunshine, in contrast, displays a positive association with incidence of the disease. Our control variables also yield interesting insights. Higher incidence is associated with higher GDP per capita and presence of mass transit systems in the province; in contrast, population density and percentage of older adults display negative associations with incidence of COVID-19.    
journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Introduction
==========================

@@

Context and Data
============

## Covid-19 in Spain

@@

## Selection of Variables

@@

## Data

@@

Methods: the Spatial SUR Model
===================

@@

Analysis
===================

## Exploratory Data Analysis

@@

# Plot
ggplot(data = env.summary, 
       aes(x = CCAA,
           y = Value)) +
  geom_boxplot() +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Autonomous Community (sorted from north to south)") +
  ylab("Value") +
  facet_wrap(~ Variable, nrow = 3, 
             scales = "free_y")
```

@@

```{r daily-correlations, echo=FALSE, fig.cap="\\label{fig:daily-correlations}Distribution of daily correlations of the independent variables with daily incidence of COVID-19 (all variables have been log-transformed)", cache = TRUE}
covid19_spain %>% 
  group_by(Date) %>%
  summarize(Older = cor(log(Older), log(Incidence)),
            GDPpc = cor(log(GDPpc), log(Incidence)),
            Density = cor(log(Density), log(Incidence)),
            Humidity_lag8 = cor(Humidity_lag8, Incidence),
            Humidity_lag11 = cor(log(Humidity_lag11), log(Incidence)),
            Humidity_lag11w = cor(log(Humidity_lag11w), log(Incidence)),
            Mean_Temp_lag8 = cor(log(Mean_Temp_lag8), log(Incidence)),
            Mean_Temp_lag11 = cor(log(Mean_Temp_lag11), log(Incidence)),
            Mean_Temp_lag11w = cor(log(Mean_Temp_lag11w), log(Incidence)),
            Sunshine_Hours_lag8 = cor(log(Sunshine_Hours_lag8 + 0.1), log(Incidence)),
            Sunshine_Hours_lag11 = cor(log(Sunshine_Hours_lag11 + 0.1), log(Incidence)),
            Sunshine_Hours_lag11w = cor(log(Sunshine_Hours_lag11w + 0.1), log(Incidence))) %>%
  select(-Date) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Correlation") %>%
  mutate(Variable = factor(Variable,
                           levels = c("GDPpc", 
                                      "Older", 
                                      "Density", 
                                      "Humidity_lag8",
                                      "Humidity_lag11",
                                      "Humidity_lag11w",
                                      "Mean_Temp_lag8",
                                      "Mean_Temp_lag11",
                                      "Mean_Temp_lag11w",
                                      "Sunshine_Hours_lag8",
                                      "Sunshine_Hours_lag11",
                                      "Sunshine_Hours_lag11w"))) %>%
  ggplot(aes(x = Variable, y = Correlation)) +
  geom_boxplot() +
  theme_tufte() +
  theme(axis.text.x = element_text(angle = 90))
```

## SUR Models

@@

For estimation, we log-transform the dependent and quantitative independent variables. The only variable that is not transformed is the categorical variable for transity systems. A log-log transformation is appropriate to capture non-linear relationships between variables and provides a straightforward interpretation of the coefficients as percentage change. Furthermore, we introduce restrictions so that the coefficients of two of our control variables are constant over time, namely GDP per capita and percentage of older adults. We do not see an  *a priori* reason to let those two variables vary across equations, and the correlation analysis in Figure \ref{fig:daily-correlations} also suggest little temporal variation. In contrast, we let the spatial autocorrelation parameter, as well as the parameters of the rest of the independent variables (including the constant) to vary over time\footnote{We conducted sensitivity analysis letting all parameters vary over time, and while the results are qualitatively similar, the resulting models are less parsimonious. These results are available in the source R markdown document.}.

@@

Results and Discussion
===================

Table \ref{tab:summary-best-model} presents a summary.

@@

Figure \ref{fig:results-time-1} shows the temporal evolution of the spatial autocorrelation coefficient ($\rho$) and the intercept of the model.

@@

Figure \ref{fig:beta-controls-time} shows the temporal evolution of the coefficients for the two control variables that were not fixed over time, i.e., $\log(Density)$ and $Transit$.

@@

```{r beta-environmenta-time, echo=FALSE, fig.height= 7, fig.cap="\\label{fig:beta-environmental-time}Temporal evolution of coefficient for the environmental variables; dots are the point estimates and vertical lines are 95% confidence intervals. In yellow is the period after the declaration of the state of emergency, and in orange is the period when only essential activities were allowed.", cache = TRUE}
# Humidity
humidity.plot <- plot_coeff(model = best_model, n = 4) + 
  ylab("Beta (log[Humidity])") +
  theme(legend.position = "none")

@@

# Sunshine
sunshine.plot <- plot_coeff(model = best_model, n = 6) + 
  ylab("Beta (log[Sunshine + 0.1])") +
  theme(legend.position = "none")

@@

```{r impacts, echo=FALSE, include=FALSE}
Wsur <- as(spdep::listw2mat(listw), "CsparseMatrix")
trsur <- spatialreg::trW(Wsur, type = "MC")
impacts.best_model <- impactspsur(best_model, tr = trsur,R = 1000)

@@

Concluding Remarks
===================

>>>>

---
title: A spatio-temporal analysis of the environmental correlates of COVID-19 incidence in Spain
author:
  - name: Antonio Paez
    email: paezha@mcmaster.ca
    affiliation: McMaster University
    footnote: 1
  - name: Fernando A. Lopez
    email: fernando.lopez@upct.es
    affiliation: Universidad Politecnica de Cartagena
  - name: Tatiane Menezes
    email: tatiane.menezes@ufpe.br
    affiliation: Departamento de Economia
  - name: Renata Cavalcanti
    email: renata.vcsantos@gmail.com
    affiliation: Nucleo de Pesquisa
  - name: Maira Galdino da Rocha Pitta
    email: mgrpitta@ufpe.br
    affiliation: Nucleo de Pesquisa
address:
  - code: McMaster University
    address: School of Geography and Earth Sciences, McMaster University, 1281 Main St W, Hamilton, ON, L8S 4K1, Canada
  - code: Universidad Politecnica de Cartagena
    address: Departamento de Metodos Cuantitativos, Ciencias Juridicas, y Lenguas Modernas, Universidad Politecnica de Cartagena, Calle Real Numero 3, 30201, Cartagena, Murcia, Spain
  - code: Departamento de Economia
    address: Departamento de Economia, Universidade Federal de Pernambuco, Av dos Economistas, s/n - Cidade Universitária, Recife - PE, 50670-901, Brasil  
  - code: Nucleo de Pesquisa
    address: Núcleo de Pesquisa em Inovação Terapêutica NUPIT / UFPE, Av. Prof. Moraes Rego, 1235 - Cidade Universitária, Recife, PE, CEP 50670-901, Brazil  
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  Spreading with astonishing speed, the novel SARS-CoV2 has swept the globe, causing enormous stress to health systems and prompting social distance guidelines and mandates to arrest its progress. While there is encouraging evidence that early public health interventions have slowed the spread of the virus, this has come at a high cost as the global economy is brought to its knees. How and when to ease restrictions to movement hinges in part on the question whether SARS-CoV2 will display seasonality associated with variations in temperature, humidity, and hours of sunshine. In this research, we address this question by means of a spatial analysis of the incidence of COVID-19 in the provinces in Spain. Use of a spatial Seemingly Unrelated Regressions (SUR) approach allows us to model the incidence of reported cases of the disease per 100,000 population, as a function of temperature and humidity, while controlling for GDP per capita, population density, percentage of older adults in the population, and presence of mass transit systems. An interesting aspect of the spatial SUR approach is that it models incidence as a contagion process. Our results indicate that incidence of the disease is lower at higher temperatures and higher levels of humidity, although coefficients for this variable are significant only in some equations. Sunshine, in contrast, displays a positive association with incidence of the disease. Our control variables also yield interesting insights. Higher incidence is associated with higher GDP per capita and presence of mass transit systems in the province; in contrast, population density and percentage of older adults display negative associations with incidence of COVID-19.    
journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: References.bib
#linenumbers: true
numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
---

@@

Introduction {#introduction}
==========================

@@

Context and Data {#context-and-data}
============

## Covid-19 in Spain {#covid-19-in-spain}

@@

## Selection of Variables {#variables}

@@

## Data {#data}

@@

Methods: the Spatial SUR Model {#methods}
===================

@@

A note regarding the interpretation of the model is in order. It is well-known that coefficients in linear regression models are partial derivatives of the dependent variable with respect to the independent variables, and therefore directly give the marginal effects or rates of change. Spatially lagged models, however, are no longer linear. The intuition behind the non-linearity is that the spatial lag expands the information set to include information from neighbouring regions: in other words, the value of an explanatory variable in a spatial unit can have influence in other spatial units via the spatial lag. This makes interpretation of the coefficients less straightforward but also richer [@Golgher2016interpret]. The results of LeSage [-@LeSage2009introduction] for cross-sectional spatial lag models can be extended to the spatial SUR framework. Note that, according to Elhorst [-@Elhorst2014spatial], the partial derivatives have the following interpretation: if an explanatory variable ($X_k$) in a particular province changes, not only the incidence rate in that province changes, also incidence rates in other provinces change via the contagion effect. Therefore, a change in $X_k$ in a particular province has a *direct effect* on that province, but also an *indirect effect* on neighbouring provinces. In this way, the $i$th diagonal element of the matrix of partial derivatives represents the direct effect on the $i$th province, whereas the non-diagonal elements of $i$th row of the matrix of partial derivatives represent the indirect effects on other provinces. In order to obtain a global indicator, the direct effect is calculated as the mean of the diagonal elements and captures the average change in incidence ratio caused by the change in $X_k$. Likewise, a global indicator of the indirect effects is calculated as the mean of the non-diagonal elements. The total effect is the sum of direct and indirect effects. Finally, note that if $\rho_k = 0$, the indirect effects are 0 and the direct effects are equal to $\beta_kt$.

Analysis {#analysis}
===================

## Exploratory Data Analysis {#eda}

@@

# Plot
ggplot(data = env.summary, 
       aes(x = CCAA,
           y = Value)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  xlab("Autonomous Community (sorted from north to south)") +
  ylab("Value") +
  facet_wrap(~ Variable, nrow = 3, 
             scales = "free_y")
```

@@

```{r daily-correlations, echo=FALSE, fig.cap="\\label{fig:daily-correlations}Distribution of daily correlations of the independent variables with daily incidence of COVID-19 (all variables have been log-transformed)", cache = TRUE}
covid19_spain %>% 
  group_by(Date) %>%
  summarize(Older = cor(log(Older), log(Incidence)),
            GDPpc = cor(log(GDPpc), log(Incidence)),
            Density = cor(log(Density), log(Incidence)),
            Humidity_lag8 = cor(Humidity_lag8, Incidence),
            Humidity_lag11 = cor(log(Humidity_lag11), log(Incidence)),
            Humidity_lag11w = cor(log(Humidity_lag11w), log(Incidence)),
            Mean_Temp_lag8 = cor(log(Mean_Temp_lag8), log(Incidence)),
            Mean_Temp_lag11 = cor(log(Mean_Temp_lag11), log(Incidence)),
            Mean_Temp_lag11w = cor(log(Mean_Temp_lag11w), log(Incidence)),
            Sunshine_Hours_lag8 = cor(log(Sunshine_Hours_lag8 + 0.1), log(Incidence)),
            Sunshine_Hours_lag11 = cor(log(Sunshine_Hours_lag11 + 0.1), log(Incidence)),
            Sunshine_Hours_lag11w = cor(log(Sunshine_Hours_lag11w + 0.1), log(Incidence))) %>%
  select(-Date) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Correlation") %>%
  mutate(Variable = factor(Variable,
                           levels = c("GDPpc", 
                                      "Older", 
                                      "Density", 
                                      "Humidity_lag8",
                                      "Humidity_lag11",
                                      "Humidity_lag11w",
                                      "Mean_Temp_lag8",
                                      "Mean_Temp_lag11",
                                      "Mean_Temp_lag11w",
                                      "Sunshine_Hours_lag8",
                                      "Sunshine_Hours_lag11",
                                      "Sunshine_Hours_lag11w"))) %>%
  ggplot(aes(x = Variable, y = Correlation)) +
  geom_boxplot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))
```

## SUR Models {#sur-models}

@@

For estimation, we log-transform the dependent and quantitative independent variables. The only variable that is not transformed is the categorical variable for transity systems. A log-log transformation is appropriate to capture non-linear relationships between variables and provides a straightforward interpretation of the coefficients as percentage change. Furthermore, we introduce restrictions so that the coefficients of two of our control variables are constant over time, namely GDP per capita and percentage of older adults. We do not see an  *a priori* reason to let those two variables vary across equations, and the correlation analysis in Figure \ref{fig:daily-correlations} also suggest little temporal variation. In contrast, we let the spatial autocorrelation parameter, as well as the parameters of the rest of the independent variables (including the constant) to vary over time\footnote{We conducted sensitivity analysis letting all parameters vary over time, and while the results are qualitatively similar, the resulting models are less parsimonious. These results are available in the source R markdown document.}. This will be useful to detect whether there are behavioral adaptations at the population level over the course of the period examined. As an example of behavioral adaptations, the effect of density might weaken over time, in the measure that the effects of the lockdown are felt: at full compliance with the lockdown, with people practicing social avoidance, density might matter less than other factors.

@@

Results and Discussion {#results-and-discussion}
===================

Table \ref{tab:summary-best-model} presents a summary of the results of Model 2 (*lag11*). Recall that two coefficients were constrained and are estimated only for the first equation of the system, and thus are assumed to be constant over time. These are the coefficients corresponding to GDP per capita and percentage of older adults. Both coefficients are significant at $p<=0.05$. The sign of the coefficient for GDP per capita is positive, which indicates that wealthier regions tend to have a higher incidence of COVID-19. This is in line with the idea that the epidemic started earlier in wealthier places due to their connections to a globalized world. The sign of the coefficient for percentage of older adults, on the other hand, is negative. As previously discussed, the level of social contact of older adults even under normal circumstances tends to be lower than for younger people. As a consequence, places with larger populations of older adults appear to have a natural level of social distancing in place. It is important to note that this does not detract from evidence that older adults are more vulnerable individually and in institutional settings, where their case mortality rates are perhaps the highest of all age groups. Instead, this result indicates that their presence in the community at large tends to depress transmission of the virus.

Of the two other control variables, the coefficient of population density is significant at $p<=0.05$ in 11 equations, and not significant in 19. The coefficient for transit is significant at $p<=0.10$ in 22 equations, and of those, significant at $p<=0.05$ in 14 equations. The next four variables are environmental factors. The coefficient for humidity is significant at $p<=0.10$ in 20 equations, and of those, significant at $p<=0.05$ in 19 equations. Of the environmental variables, temperature is the only variable that has significant coefficients in every equation at $p<=0.05$. Finally, sunshine has significant coefficients at $p<=0.10$ in 18 equations, including 15 coefficients that are significant at $p<=0.05$.

@@

To better understand the results, we proceed to plot the coefficients in their temporal sequence. We begin with the evolution of the spatial autocorrelation coefficient ($\rho$) and the intercept of the model, both of which are shown in Figure \ref{fig:results-time-1}.

@@

Figure \ref{fig:beta-controls-time} shows the temporal evolution of the coefficients for the two control variables that were not fixed over time, i.e., $\log(Density)$ and $Transit$. In Section \ref{variables} we had anticipated a positive sign for the coefficient of this variable. The negative sign in the results is therefore somewhat surprising. Upon reflection, however, it seems reasonable that the sign would be negative during the period under analysis.

@@

```{r beta-environmental-time, echo=FALSE, fig.height= 7, fig.cap="\\label{fig:beta-environmental-time}Temporal evolution of coefficient for the environmental variables; dots are the point estimates and vertical lines are 95% confidence intervals. In yellow is the period after the declaration of the state of emergency, and in orange is the period when only essential activities were allowed.", cache = TRUE}
# Humidity
humidity.plot <- plot_coeff(model = best_model, n = 4) + 
  ylab("Beta (log[Humidity])") +
  theme(legend.position = "none")

@@

# Sunshine
sunshine.plot <- plot_coeff(model = best_model, n = 6) + 
  ylab("Beta (log[Sunshine])") +
  theme(legend.position = "none")

@@

```{r impacts, evalcho=FALSE, include=FALSE}
Wsur <- as(spdep::listw2mat(listw), "CsparseMatrix")
trsur <- spatialreg::trW(Wsur, type = "MC")
impacts.best_model <- impactspsur(best_model, tr = trsur,R = 1000)

@@

```{r calculate-impacts-best-model, echo=FALSE, cache = TRUE}
# Calculate impacts
Wsur <- as(spdep::listw2mat(listw), "CsparseMatrix")
trsur <- spatialreg::trW(Wsur, type = "MC")
best_model.impacts <- impactspsur(best_model, tr = trsur,R = 1000)

# Organize in dataframe
best_model.impacts <- data.frame(Impact = unlist(best_model.impacts)) %>%
  # Identify point estimates of effects for each variable and simulated values 
  mutate(Variable = c(c(rep(c("log(GDPpc)", 
                              "log(Older)",
                              "log(Density)",
                              "Transit",
                              "log(Humidity)",
                              "log(Temperature)",
                              "log(Sunshine)"),
                            3),
                        rep("junk", 21000)),
                      rep(c(rep(c("log(Density)",
                                  "Transit",
                                  "log(Humidity)",
                                  "log(Temperature)",
                                  "log(Sunshine)"),
                                3),
                            rep("junk", 15000)), # These are the simulated values
                          29))) %>%
  filter(Variable != "junk") %>% # Remove all simulations, keep only point estimates
  # Add type of effect and date
  mutate(Type = c(rep(c("Direct", 
                        "Indirect", 
                        "Total"),
                      each = 7),
                  rep(rep(c("Direct", 
                            "Indirect", 
                            "Total"),
                          each = 5),
                      29)),
         Date = c(rep(ymd("2020-03-13"),
                      21),
                  rep(seq(ymd("2020-03-14"),
                          ymd("2020-04-11"), 
                          by = "days"), 
                      each = 15))) %>%
  # Convert to factors
  mutate(Variable = factor(Variable,
                           levels = c("log(GDPpc)", 
                              "log(Older)",
                              "log(Density)",
                              "Transit",
                              "log(Humidity)",
                              "log(Temperature)",
                              "log(Sunshine)")),
         Type = factor(Type,
                       levels = c("Direct", 
                            "Indirect", 
                            "Total")))
```

The effects of the different variables are summarized in Table \ref{tab:summary-impacts-best-model}.

```{r summary-impacts-best-model, echo=FALSE}
rbind(best_model.impacts %>%
  filter(Type == "Direct") %>%
  group_by(Variable) %>%
  summarize(Min = min(Impact), 
            Mean = mean(Impact), 
            Max = max(Impact)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")),
  best_model.impacts %>%
  filter(Type == "Indirect") %>%
  group_by(Variable) %>%
  summarize(Min = min(Impact), 
            Mean = mean(Impact), 
            Max = max(Impact)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained")),
  best_model.impacts %>%
  filter(Type == "Total") %>%
  group_by(Variable) %>%
  summarize(Min = min(Impact), 
            Mean = mean(Impact), 
            Max = max(Impact)) %>% # Number of coefficients with pval <=5 
  mutate(Note = c("Constrained", 
                  "Constrained", 
                  "Non-constrained", 
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained",
                  "Non-constrained"))) %>%
  kable("latex",
        #"html",
        booktabs = TRUE,
        digits = 3,
        col.names = c("Variable", "Min", "Mean", "Max", "Note"),
        caption = "\\label{tab:summary-impacts-best-model}Summary of direct, indirect, and total effects according to best model (lag11: lagged 11-day moving average)") %>%
  kable_styling(latex_options = c("striped")) %>%
  #kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  pack_rows("Direct Effects", 1, 7) %>%
  pack_rows("Indirect Effects", 8, 14) %>%
  pack_rows("Total Effects", 15, 21) %>%
  footnote(general = c("Non-constrained: coefficient was allowed to vary across equations",
                       "Constrained: coefficient as constant across equations"))
```

The temporal variation of the effects is shown in Figure \ref{fig:plot-impacts}.

```{r plot-impacts, echo=FALSE, fig.cap="\\label{fig:plot-impacts}Temporal evolution of effects by date; the impact is percentage change in incidence as a result of a one percent change in value of variable."}
best_model.impacts %>%
  filter(Variable != "log(GDPpc)", 
         Variable != "log(Older)") %>%
  ggplot(aes(x = Date, 
             y = Impact, 
             color = Variable)) +
  geom_line(size = 0.8) +
  scale_color_brewer(palette = "Set1") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "bottom") +
  facet_wrap(~ Type, ncol = 3)

Concluding Remarks {#conclusion}
===================
